---
title: "HollisT_Week7"
author: "Tim Hollis"
date: "`r Sys.Date()`"
output: html_document
---
Assignment:

A researcher hypothesizes that TV stimulation for kids will result in an increase in the number of pieces of candy corn eaten. The kids are subjected to 5 hours of television. The number of candy corn candies consumed during a 10-minute period is counted both with and without TV. Compute the appropriate t-test for the data provided below.



Experiment #

With TV

Without TV

1

12

8

2

7

7

3

3

4

4

11

14

5

8

6

6

5

7

7

14

12

8

7

5

9

9

5

10

10

8



What is your computed answer for the following, based on the date in the table above?




Mean =

Mean =

S =

S =

S2 =

S2 =



What is your computed t-test answer?
What is the null hypothesis in this study?
What is the alternate hypothesis?
What probability level did you choose and why?
What are your degrees of freedom?
Is there a significant difference between the two testing conditions? Interpret your answer.


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.align = 'center',
  fig.width = 6,
  fig.height = 4,
  out.width = '80%'
  )

library(knitr)
library(kableExtra)

options(
  digits = 2,
  scipen = 999
)
```


## **TV Stimulation and Candy Corn Consumption**

### **Hypothesis**

A researcher hypothesizes that TV stimulation increases candy corn consumption
in children. Each child observed under two conditions, with and without 5 hours
of TV, and the number of candies eaten in 10 minutes is recorded. We will first
calculate the mean, standard deviation, and variance of both vectors.

```{r descriptive-stats, results='asis'}

#data

with_tv <- c(12, 7, 3, 11, 8, 5, 14, 7, 9, 10)
without_tv <- c(8, 7, 4, 14, 6, 7, 12, 5, 5, 8)

# Mean

mean_with_tv <- mean(with_tv)
mean_without_tv <- mean(without_tv)

# SD

sd_with_tv <- sd(with_tv)
sd_without_tv <- sd(without_tv)

# Variance

var_with_tv <- var(with_tv)
var_without_tv <- var(without_tv)
```

### **R-Markdown, then R-Chunk summary tables**

| Condition     | Mean                | SD                  | Variance             |
|:-------------:|:------------------:|:-------------------:|:--------------------:|
| With TV       | `r mean_with_tv`    | `r sd_with_tv`       | `r var_with_tv`      |
| Without TV    | `r mean_without_tv` | `r sd_without_tv`    | `r var_without_tv`   |

```{r summary-table}
# Create the summary table

stats_table <- data.frame(
  Condition = c('With TV', 'Without TV'),
  Mean = c(mean_with_tv, mean_without_tv),
  SD = c(sd_with_tv, sd_without_tv),
  Variance = c(var_with_tv, var_without_tv)
)

# Render with borders and centered alignment

kable(stats_table, align = 'c') %>%
  kable_styling(full_width = FALSE, position = 'center', bootstrap_options = c('striped', 'bordered'))
```


#### **Summary**

The descriptive statistics suggest that children consumed minimally more candy 
corn on average after watching TV (`r mean_with_tv`) compared to without TV 
(`r mean_without_tv`). The variability in both conditions is relatively similar,
as shown by the standard deviations and variances.

To determine whether this observed difference is statistically significant, we 
will now conduct a paired-sample t-test.

### **Paired t-test Analysis**

```{r paired-t-test}

# Conduct paired t-test

t_test_result <- t.test(with_tv, without_tv, paired = TRUE)
t_test_result
```

#### **Summary: Interpretation of t-test Results**

- **Null Hypothesis (H₀):** There is no difference in candy corn consumption 
between the TV and no-TV conditions.
- **Alternative Hypothesis (H₁):** Candy corn consumption increases after TV 
stimulation.
- **Significance Level (α):** 0.05, chosen as a conventional threshold for 
detecting meaningful effects.
- **Degrees of Freedom:** `r t_test_result$parameter`
- **t-statistic:** `r round(t_test_result$statistic, 3)`
- **p-value:** `r round(t_test_result$p.value, 4)`

Since the p-value is `r round(t_test_result$p.value, 4)`, which is greater than 
0.05, we **fail to reject the null hypothesis**. This suggests that TV 
stimulation **does not have a statistically significant effect** on candy corn 
consumption. While there's a small observed difference in means (8.6 vs 7.6), 
this difference is not statistically significant and could easily occur by 
random chance

### **Visual Comparison**


```{r boxplot-visual}

# data
means <- c(mean(with_tv), mean(without_tv))
overall_mean <- mean(c(with_tv, without_tv))

# Create the boxplot
boxplot(with_tv, without_tv,
        names = c('With TV', 'Without TV'),
        col = c('orange', 'lightblue'),
        main = 'Candy Corn Consumption by Condition',
        ylab = 'Pieces Eaten',
        ylim = c(0, 20))


# Add dashed line for overall mean
abline(h = overall_mean, col = 'darkgreen', lty = 2)

# Add mini legend in top right
legend('topright',
       legend = c('Group Mean', 'Overall Mean'),
       col = c('black', 'darkgreen'),
       lty = c(1, 2),
       pch = c(NA, NA),
       bty = 'n',
       cex = 0.8)
```


#### **Summary**

The paired t-test revealed no significant increase in candy corn consumption 
after TV exposure. This fails to support the researchers assumption that TV 
exposure has a significant impact on candy corn consumption.



## **Reflection on Week’s Learning**

**What felt intuitive:** 

- Setting up the data vectors and calculating descriptive statistics felt 
straightforward and reinforced my understanding of basic R functions.

**What was challenging:** 

- Interpreting the t-test output and remembering the assumptions of paired tests
required a bit more review. I will be honest, I originally interpreted the 
alternate hypothesis as being correct based on the difference between the means 
being 1 and not 0, but had to reword and resubmit my assignment when I finally
factored in the p-value of .22 being higher than .05, so theres a 22% chance, 
the means being greater than 0, is random and based on sample size!

**What I’ll stop doing:** 

- Relying solely on visual inspection without statistical testing, the t-test 
added clarity and confidence to the interpretation. I will also ensure that my
interpretation of data is inclusive of all factors included and not jump to a 
conclusion based on one factor.

**What I’ll continue doing:** 

- Using both Markdown and styled R tables for clarity, and incorporating visuals
to support statistical findings.
