---
title: "HollisT_Week1"
author: "Tim Hollis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$s#et(echo = TRUE)
```

## Week 1 Markdown
## Tim Hollis


This section was originally (as were all of them), completed separately in the console, with my Markdown remaining unedited, so this is the second time completing all of the code below, and the third time for a lot of it - though practicing through repetition, is not a terrible thing to do!

For this assignment, it was pretty straight forward, there were times in the console I tried different formats such as not placing the code on different lines and combining it into one sentence like structure, but found that to give me an error especially when completing the "if/else" "while" and other functions similar, so began following the W3 tutorial guidance exactly to avoid those errors which is what I am doing with the code in my R Markdown.

I did not add the comments to each of the coding activities, as you are already aware of what it is we are submitting, and I did not recreate the errors as I understand the concept, so any errors you see are actual errors I made like when I tried to say my age was "28 till I die" and then changed it to my actual age on my birth certificate.

For me the matrix and the ability to use coding to find specific metrics in a large data set were the most intriguing, looking for the lowest HP manually in the listed cars would take quite awhile, which could add to the risk of inaccurately assessing that data whereas using the code is instant and infallible as long as it is executed properly.

As the Motor Trends populates an internal page, I am including the public URL for that information [Here](https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars)



```{r}
"Hello World!"
5
10
25
5 + 5
for (x in 1:10) {
  print(x)
}
# The commenting with the hashtag is not difficult to remember, but for the most part, I will leave them out of my R Markdown, since you will be aware of what I am doing without the need for explanation.
# Just to make 
# sure I show the concept
# of writing comments on multiple lines
# I am doing this example
"Hello World!"
name<-"Tim"
age<-37
print(name)
print(age)
name<-"Tim Hollis"
print(name)
for (x in 1:10) {
  print(x)
}
text <- "awesome"
paste("R is", text)
text1 <- "R is"
text2 <- "awesome"
paste(text1, text2)
num1 <- 5
num2 <- 10
num1 + num2
var1 <- var2 <- var3 <- "Orange"
var1
var2
var3
my_var <- 30
my_var <- "Jebediah"
x <- 10.5
class(x)
x <- 1000L
class(x)
x <- 9i + 3
class(x)
x <- "R is exciting"
class(x)
x <- TRUE
class(x)
x <- 10.5
y <- 10L
z <- 1i
x <- 10.5
y <- 55
print(x) # I like consistency so tend to use the print function when writing as it is common in Python, so I tend to add that in R as well many times instead of simply placing the value after assignment is given to that value
print(y)
class(x)
class(y)
x <- 1000L
y <- 55L
print(x)
print(y)
class(x)
class(y)
x <- 3+5i
y <- 5i
print(x)
print(y)
class(x)
class(y)
x <- 1L
y <- 2
a <- as.numeric(x)
b <- as.integer(y)
print(x)
print(y)
class(a)
class(b)
10 + 5
10 - 5
max(5, 10, 15)
min(5, 10, 15)
sqrt(16)
abs(-4.7)
ceiling(1.4)
floor(1.4)
str<-"Hello"
print(str)
str<-"There was a farmer,
who had a dog,
and Bingo was his name-o,
B-I-N-G-O!"
print(str)
cat(str)
nchar(str)
grepl("H", str)
grepl("had", str)
grepl("X", str)
str1 <- "Hello"
str2 <- "World"
paste(str1, str2)
str<-"I wish I was a \"Blanche\" but unfortunately, I am more of a \"Dorothy\" whem it comes to real life!"
str
cat(str)
10 > 9
10 == 9
10 < 9
a <- 10
b <- 9
a > b
a <- 200
b <- 33
if (b > a) {
  print ("b is greater than a")
} else {
  print("b is not greater than a")
}
10+5
10-5
10*5
10/5
10^5
10%%5
10%/%5
my_var <- 3
print(my_var)
my_var <<- 3
print(my_var)
3 -> my_var
print(my_var)
3 ->> my_var
print(my_var)
10==5
10!=5
10>5
10<5
10>=5
10<=5
a <- 33
b <- 200
if (b > a) {
  print("b is greater than a")
}
a <- 33
b <- 33
if (b > a) {
  print("b is greater than a")
} else if (a == b) {
  print ("a and b are equal")
}
a <- 200
b <- 33
if (b > a) {
  print("b is greater than a")
} else if (a == b) {
  print("a and b are equal")
} else {
  print("a is greater than b")
}
a <- 200
b <- 33
if (b > a) {
  print("b is greater than a")
} else {
  print("b is not greater than a")
}
x <- 41
if (x > 10) {
  print("Above ten")
  if (x > 20) {
    print("and also above 20!")
  } else {
    print("but not above 20.")
  }
} else {
  print("below 10.")
}
a <- 200
b <- 33
c <- 500
if (a > b & c > a) {
  print("Both conditions are true")
}
a <- 200
b <- 33
c <- 500
if (a > b | a > c) {
  print("At least one of the conditions is true")
}
i <- 1
while (i < 6) {
  print(i)
  i <- i + 1
}
i <- 1
while (i < 6) {
  print(i)
  i <- i + 1
  if (i == 4) {
    break
  }
}
i <- 0
while (i < 6) {
  i <- i + 1
  if (i == 3) {
    next
  }
  print(i)
}
dice <- 1
while (dice <= 6) {
  if (dice < 6) {
    print("No Yahtzee")
  } else {
    print("Yahtzee!")
  }
  dice <- dice + 1
}
for (x in 1:10) {
  print(x)
}
fruits <- list("apple", "banana", "cherry")
for (x in fruits) {
  print(x)
}
dice <- c(1, 2, 3, 4, 5, 6)
for (x in dice) {
  print(x)
}
fruits <- list("apple", "banana", "cherry")
for (x in fruits) {
  if (x == "cherry") {
    break
  }
  print(x)
}
fruits <- list("apple", "banana", "cherry")
for (x in fruits) {
  if (x == "banana") {
    next
  }
  print(x)
}
dice <- 1:6
for(x in dice) {
  if (x == 6) {
    print(paste("The dice number is", x, "Yahtzee!"))
  } else {
    print(paste("The dice number is", x, "Not Yahtzee"))
  }
}
adj <- list("red", "big", "tasty")
fruits <- list("apple", "banana", "cherry")
  for (x in adj) {
    for (y in fruits) {
      print(paste(x, y))
  }
  }
my_function <- function() { # create a function with the name my_function
  print("Hello World!")
}
my_function <- function() {
  print("Hello World!")
}
my_function()
my_function <- function(fname) {
  paste(fname, "Griffin")
}
my_function("Peter")
my_function("Lois")
my_function("Stewie")
my_function <- function(fname, lname) {
  paste(fname, lname)
}
my_function("Peter", "Griffin")
my_function <- function(country = "USA") {
  paste("I am from", country)
}
my_function("Sweden")
my_function("India")
my_function("Norway")
my_function()
my_function <- function(x) {
  return (5 * x)
}
print(my_function(3))
print(my_function(5))
print(my_function(9))
Nested_function <- function(x, y) {
  a <- x + y
  return(a)
}
Nested_function(Nested_function(2,2), Nested_function(3,3))
Outer_func <- function(x) {
  Inner_func <- function(y) {
    a <- x + y
    return(a)
  }
  return (Inner_func)
}
output <- Outer_func(3)
output(5)
tri_recursion <- function(k) {
  if (k > 0) {
    result <- k + tri_recursion(k - 1)
    print(result)
  } else {
    result = 0
    return(result)
  }
}
tri_recursion(6)
txt <- "awesome"
my_function <- function() {
  paste("R is", txt)
}
my_function()
txt <- "global variable"
my_function <- function() {
  txt = "fantastic"
  paste("R is", txt)
}
my_function()
print(txt)
my_function <- function() {
txt <<- "fantastic"
  paste("R is", txt)
}
my_function()
print(txt)
txt <- "awesome"
my_function <- function() {
  txt <<- "fantastic"
  paste("R is", txt)
}
my_function()
paste("R is",txt)
fruits <- c("banana", "apple", "orange")
print(fruits)
thislist <- list("apple", "banana", 50, 100)
print(thislist)
thismatrix <- matrix(c(1,2,3,4,5,6), nrow = 3, ncol = 2)
print(thismatrix)
thisarray <- c(1:24)
print(thisarray)
multiarray <- array(thisarray, dim = c(4, 3, 2))
print(multiarray)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
print(Data_Frame)
fruits <- c("banana", "apple", "orange")
print(fruits)
numbers <- c(1, 2, 3)
print(numbers)
numbers <- 1:10
print(numbers)
numbers1 <- 1.5:6.5
print(numbers1)
numbers2 <- 1.5:6.3
print(numbers2)
log_values <- c(TRUE, FALSE, TRUE, FALSE)
print(log_values)
fruits <- c("banana", "apple", "orange")
length(fruits)
fruits <- c("banana", "apple", "orange", "mango", "lemon")
numbers <- c(13, 3, 5, 7, 20, 2)
sort(fruits)
sort(numbers)
fruits <- c("banana", "apple", "orange")
fruits[1]
fruits <- c("banana", "apple", "orange", "mango", "lemon")
fruits[c(1, 3)]
fruits <- c("banana", "apple", "orange", "mango", "lemon")
fruits[c(-1)]
fruits <- c("banana", "apple", "orange", "mango", "lemon")
fruits[1] <- "pear"
print(fruits)
repeat_each <- rep(c(1,2,3), each = 3)
print(repeat_each)
repeat_times <- rep(c(1,2,3), times = 3)
print(repeat_times)
repeat_indepent <- rep(c(1,2,3), times = c(5,2,1))
print(repeat_indepent)
numbers <- 1:10
print(numbers)
numbers <- seq(from = 0, to = 100, by = 20)
print(numbers)
thislist <- list("apple", "banana", "cherry")
print(thislist)
thislist <- list("apple", "banana", "cherry")
print(thislist[1])
thislist <- list("apple", "banana", "cherry")
thislist[1] <- "blackcurrant"
print(thislist)
thislist <- list("apple", "banana", "cherry")
length(thislist)
thislist <- list("apple", "banana", "cherry")
"apple" %in% thislist
thislist <- list("apple", "banana", "cherry")
append(thislist, "orange")
thislist <- list("apple", "banana", "cherry")
append(thislist, "orange", after = 2)
thislist <- list("apple", "banana", "cherry")
newlist <- thislist[-1]
print(newlist)
thislist <- list("apple", "banana", "cherry", "orange", "kiwi", "melon", "mango")
(thislist)[2:5]
thislist <- list("apple", "banana", "cherry")
for (x in thislist) {
  print(x)
}
list1 <- list("a", "b", "c")
list2 <- list(1,2,3)
list3 <- c(list1,list2)
print(list3)
thismatrix <- matrix(c(1,2,3,4,5,6), nrow = 3, ncol = 2)
print(thismatrix)
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
print(thismatrix)
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
print(thismatrix[1,2])
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
print(thismatrix[2,])
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
print(thismatrix[,2])
thismatrix <- matrix(c("apple", "banana", "cherry", "orange","grape", "pineapple", "pear", "melon", "fig"), nrow = 3, ncol = 3)
thismatrix[c(1,2),]
thismatrix <- matrix(c("apple", "banana", "cherry", "orange","grape", "pineapple", "pear", "melon", "fig"), nrow = 3, ncol = 3)
thismatrix[, c(1,2)]
thismatrix <- matrix(c("apple", "banana", "cherry", "orange","grape", "pineapple", "pear", "melon", "fig"), nrow = 3, ncol = 3)
newmatrix <- cbind(thismatrix, c("strawberry", "blueberry", "raspberry"))
print(newmatrix)
thismatrix <- matrix(c("apple", "banana", "cherry", "orange","grape", "pineapple", "pear", "melon", "fig"), nrow = 3, ncol = 3)
newmatrix <- rbind(thismatrix, c("strawberry", "blueberry", "raspberry"))
print(newmatrix)
thismatrix <- matrix(c("apple", "banana", "cherry", "orange", "mango", "pineapple"), nrow = 3, ncol =2)
thismatrix <- thismatrix[-c(1), -c(1)]
print(thismatrix)
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
"apple" %in% thismatrix
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
dim(thismatrix)
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
length(thismatrix)
thismatrix <- matrix(c("apple", "banana", "cherry", "orange"), nrow = 2, ncol = 2)
for (rows in 1:nrow(thismatrix)) {
  for (columns in 1:ncol(thismatrix)) {
    print(thismatrix[rows, columns])
  }
}
Matrix1 <- matrix(c("apple", "banana", "cherry", "grape"), nrow = 2, ncol = 2)
Matrix2 <- matrix(c("orange", "mango", "pineapple", "watermelon"), nrow = 2, ncol = 2)
Matrix_Combined <- rbind(Matrix1, Matrix2)
print(Matrix_Combined)
Matrix_Combined <- cbind(Matrix1, Matrix2)
print(Matrix_Combined)
thisarray <- c(1:24)
print(thisarray)
multiarray <- array(thisarray, dim = c(4, 3, 2))
print(multiarray)
thisarray <- c(1:24)
multiarray <- array(thisarray, dim = c(4, 3, 2))
multiarray[2, 3, 2]
thisarray <- c(1:24)
multiarray <- array(thisarray, dim = c(4, 3, 2))
multiarray[c(1),,1]
multiarray <- array(thisarray, dim = c(4, 3, 2))
multiarray[,c(1),1]
thisarray <- c(1:24)
multiarray <- array(thisarray, dim = c(4, 3, 2))
2 %in% multiarray
thisarray <- c(1:24)
multiarray <- array(thisarray, dim = c(4, 3, 2))
dim(multiarray)
thisarray <- c(1:24)
multiarray <- array(thisarray, dim = c(4, 3, 2))
length(multiarray)
thisarray <- c(1:24)
multiarray <- array(thisarray, dim = c(4, 3, 2))
for(x in multiarray){
  print(x)
}
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
print(Data_Frame)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
print(Data_Frame)
summary(Data_Frame)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
Data_Frame[1]
Data_Frame[["Training"]]
Data_Frame$Training
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
New_row_DF <- rbind(Data_Frame, c("Strength", 110, 110))
print(New_row_DF)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
New_col_DF <- cbind(Data_Frame, Steps = c(1000, 6000, 2000))
print(New_col_DF)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
Data_Frame_New <- Data_Frame[-c(1), -c(1)]
print(Data_Frame_New)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
dim(Data_Frame)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
ncol(Data_Frame)
nrow(Data_Frame)
Data_Frame <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
length(Data_Frame)
Data_Frame1 <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
Data_Frame2 <- data.frame (
  Training = c("Stamina", "Stamina", "Strength"),
  Pulse = c(140, 150, 160),
  Duration = c(30, 30, 20)
)
New_Data_Frame <- rbind(Data_Frame1, Data_Frame2)
print(New_Data_Frame)
Data_Frame3 <- data.frame (
  Training = c("Strength", "Stamina", "Other"),
  Pulse = c(100, 150, 120),
  Duration = c(60, 30, 45)
)
Data_Frame4 <- data.frame (
  Steps = c(3000, 6000, 2000),
  Calories = c(300, 400, 300)
)
New_Data_Frame1 <- cbind(Data_Frame3, Data_Frame4)
print(New_Data_Frame1)
music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock", "Jazz"))
print(music_genre)
music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock", "Jazz"))
levels(music_genre)
music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock", "Jazz"), levels = c("Classic", "Jazz", "Pop", "Rock", "Other"))
levels(music_genre)
music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock", "Jazz"))
length(music_genre)
music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock", "Jazz"))
music_genre[3]
music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock", "Jazz"))
music_genre[3] <- "Pop"
music_genre[3]
music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock", "Jazz"), levels = c("Classic", "Jazz", "Pop", "Rock", "Opera"))
music_genre[3] <- "Opera"
music_genre[3]
plot(1, 3)
plot(c(1, 8), c(3, 10))
plot(c(1, 2, 3, 4, 5), c(3, 7, 8, 9, 12))
x <- c(1, 2, 3, 4, 5)
y <- c(3, 7, 8, 9, 12)
plot(x, y)
plot(1:10)
plot(1:10, type="l")
plot(1:10, main="My Graph", xlab="The x-axis", ylab="The y axis")
plot(1:10, col="red")
plot(1:10, cex=2)
plot(1:10, pch=8, cex=2)
plot(1:10, type="l")
plot(1:10, type="l", col="blue")
plot(1:10, type="l", lwd=2)
plot(1:10, type="l", lwd=5, lty=3)
line1 <- c(1,2,3,4,5,10)
line2 <- c(2,5,7,8,9,10)
plot(line1, type = "l", col = "blue")
lines(line2, type="l", col = "red")
x <- c(5,7,8,7,2,2,9,4,11,12,9,6)
y <- c(99,86,87,88,111,103,87,94,78,77,85,86)
plot(x, y)
x <- c(5,7,8,7,2,2,9,4,11,12,9,6)
y <- c(99,86,87,88,111,103,87,94,78,77,85,86)
plot(x, y, main="Observation of Cars", xlab="Car age", ylab="Car speed")
x1 <- c(5,7,8,7,2,2,9,4,11,12,9,6)
y1 <- c(99,86,87,88,111,103,87,94,78,77,85,86)
x2 <- c(2,2,8,1,15,8,12,9,7,3,11,4,7,14,12)
y2 <- c(100,105,84,105,90,99,90,95,94,100,79,112,91,80,85)
plot(x1, y1, main="Observation of Cars", xlab="Car age", ylab="Car speed", col="red", cex=2)
points(x2, y2, col="blue", cex=2)
x <- c(10,20,30,40)
pie(x)
x <- c(10,20,30,40)
pie(x, init.angle = 90)
x <- c(10,20,30,40)
mylabel <- c("Apples", "Bananas", "Cherries", "Dates")
pie(x, label = mylabel, main = "Fruits")
colors <- c("blue", "yellow", "green", "black")
pie(x, label = mylabel, main = "Fruits", col = colors)
mylabel <- c("Apples", "Bananas", "Cherries", "Dates")
colors <- c("blue", "yellow", "green", "black")
pie(x, label = mylabel, main = "Pie Chart", col = colors)
legend("bottomright", mylabel, fill = colors)
x <- c("A", "B", "C", "D")
y <- c(2, 4, 6, 8)
barplot(y, names.arg = x)
x <- c("A", "B", "C", "D")
y <- c(2, 4, 6, 8)
barplot(y, names.arg = x, col = "red")
x <- c("A", "B", "C", "D")
y <- c(2, 4, 6, 8)
barplot(y, names.arg = x, density = 10)
x <- c("A", "B", "C", "D")
y <- c(2, 4, 6, 8)
barplot(y, names.arg = x, width = c(1,2,3,4))
x <- c("A", "B", "C", "D")
y <- c(2, 4, 6, 8)
barplot(y, names.arg = x, horiz = TRUE)
print(mtcars)
?mtcars # Added link in summary based on the information returned when this code is run
Data_Cars <- mtcars
dim(Data_Cars)
names(Data_Cars)
Data_Cars <- mtcars
rownames(Data_Cars)
Data_Cars <- mtcars
Data_Cars$cyl
Data_Cars <- mtcars
sort(Data_Cars$cyl)
Data_Cars <- mtcars
summary(Data_Cars)
Data_Cars <- mtcars
max(Data_Cars$hp)
min(Data_Cars$hp)
Data_Cars <- mtcars
which.max(Data_Cars$hp)
which.min(Data_Cars$hp)
Data_Cars <- mtcars
rownames(Data_Cars)[which.max(Data_Cars$hp)] # Personally I find this and the next function to be awesome features, probably my favorites that I learned this week, because when executed properly, the amount of work they reduce if you were looking at a huge amount of data, coupled with the accuracy they provide, saves time and frustration for sure!
rownames(Data_Cars)[which.min(Data_Cars$hp)]
Data_Cars <- mtcars
mean(Data_Cars$wt)
Data_Cars <- mtcars
median(Data_Cars$wt)
Data_Cars <- mtcars
names(sort(-table(Data_Cars$wt)))[1]
Data_Cars <- mtcars
quantile(Data_Cars$wt, c(0.75))
Data_Cars <- mtcars
quantile(Data_Cars$wt)
```
## Reflection

### What I Found Conceptually Easiest
- Understanding how vectors and lists work in R.
- Mirroring Python by using the print function
- Creating basic plots with `plot()` and customizing them with color and labels. This also happens to be something I enjoy regardless even when using Excel or other systems, charts excite me!

### What I Found Most Challenging
- Troubleshooting the `?mtcars` help command and figuring out how to include it in the final output.
- Remembering to close code chunks properly with three backticks, there were a couple times I was attempting to delete an extra row and accidentally brought the tickmarks to the end of a line of code and got an error when knitting.
- Understanding which functions or commands I could place all on one line, and which ones I had to break into multiple lines as shown in the W3 tutorial. I attempted to avoid any copy and pasting, and was successful for the most part though I was still simply following the exact detail I viewed, and will work to understand this better as I improve.

### What I Learned
- R Markdown requires careful formatting to knit successfully.
- HTML output is more flexible for links and visuals than PDF, my original file was in PDF, and I changed it to HTML only when my link in the summary for the ?mtcars problem, would not load properly (this could be over assimilation though based on something I tried and it not working with the PDF and then working fine in HTML).
- Even small syntax errors (like a missing variable name or stray backtick) can halt execution—but they’re fixable with patience and attention.

### What I’d Do Differently Next Time
- Break the final product into multiple chunks, and run them periodically to ensure I can pinpoint errors right away.
- If possible, find a way to clone or create redundancy in coding, though it was great practice, this was the second (actually third for most activities) time completing the same code due to incorrectly doing all coding in the console, as I had not read the instructions properly
- Show a better conceptual understanding that once a value has been assigned, I do not need to repeatedly assign it unless that value is changing, many of the examples began with the value being assigned, but the same values were already assigned in prior example so though I was following the examples literally, I do not know that added anything but unnecessary lines of code that could be avoided.

When all is said and done, I very much enjoyed this exercise, not only because I enjoy command based systems, but also because I surprised myself at how much I actually understood conceptually and how many of the steps I remembered when I completed the assessment on the W3 site, I did not believe I would understand or be able to recall so much of the information which for me means I truly enjoyed the subject matter, otherwise my brain dumps it out immediately and cheat sheets are required to be created in Excel or some other system that I can use to quiz myself!

